### 2019-12-22 article.tex
Comparison added to the end of tests

@@

>>>>

Also we tested two other methods for comparison, First Sarraf and Tofighi's method \cite{Sarraf2016} which had been described in the beginning of Section \ref{section:proposedMethod} which required a powerful GPU for calculations, had a lot of small assumptions about the data but faced overfitting in all 4 different experiments (Accuracies: [$66.67\%$ , $50\%$ , $50\%$ , $16.67\%$]). Second method is a SVM based method proposed by Rashid et al \cite{Rashid2016} for classification of schizophrenia and bipolar patients based on functional network connectivities. This method takes some assumptions about the data and is not easily expandable to other diseases but I tried it as a competitor (Accuracies: [$83.33\%$ , $66.67\%$ , $66.67\%$ , $16.67\%$]). The comparison can be seen in Table \ref{table:comparison}.

\begin{table}
	\caption{Comparison of the proposed method with 2 other rivals}
	\begin{tabular}{| c | c | c | c | }
		\hline
		Method & \shortstack{Average \\ accuracy (\%)} & \shortstack{Average \\ time (min)} & \shortstack{Test \\ hardware} \\ \hline

		Proposed Method & 97.92 & 72.06 & GPU \tiny{(GTX1080)} \\
		Sarraf and Tofighi & 45.83 & 407.6 & CPU \tiny{(Intel4710HQ)} \\
		Rashid et al.          & 58.33 & 23.13 & CPU \tiny{(Intel4710HQ)} \\ \hline
	\end{tabular}
	\label{table:comparison}
\end{table}

@@

Without
